### 2016-03-23 paper.tex
Change title
Add citation to constructionism to help justify our approach

\newcommand{\projecttitle}{Definition and directions of cultural-narrative games}

@@

Investigating the potential for culture-narration games to teach
cultural empathy brought our team into a partnership with
\textit{a local library branch hidden for blind review}. This branch
serves primarily patrons from low socio-economic status, although
its special technology education programs also draw homeschoolers from
around the region.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as a place to visit with friends, to participate in programs,
and to access technology.

@@

A team of eleven undergraduate students, working with a faculty mentor,
undertook a design experiment and pilot study to explore a monster-themed
culture-narration game.
The students' majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.

>>>>

\newcommand{\projecttitle}{The Culture-Narration Genre: Defining the genre and identifying its potential for educational games}

@@

Investigating the potential for culture-narration games to teach
cultural empathy brought our team into a partnership with
\textit{[a local library branch hidden for blind review]}. This branch
serves primarily patrons from low socio-economic status, although
its special technology education programs also draw homeschoolers from
around the region.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as a place to visit with friends, to participate in programs,
and to access technology.

@@

A team of eleven undergraduate students, working with a faculty mentor,
undertook a design experiment and pilot study to explore a monster-themed
culture-narration game;
our approach draws upon constructionist~\citep{Papert2001}
traditions, engaging in the design experiment with a multifaceted approach,
building prototypes as a way to understand them.
The students' majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.
